{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-01-29 paper/paper.tex
added conclusion

\subsection{Conclusion}

>>>>

\subsection{Conclusion}
The approach of Barthe et. al. shows how to build a framework to create type-annotated programs that can
be check statically and can be run independent of the scheduling algorithm. Thus there is no need to trust
the compiler.

In contrast to Mantel and Sudbrocks work the whole framework depends heavily on the security of the scheduler.
It is possible to choose most scheduling algorithms, but every algorithm needs to be modified satisfy the
properties for a secure scheduler. Additionally its likely that the interface of the scheduler needs to be
changed/extended in nearly ever implementation. The FSI-security instead is applicable to every robust
scheduler without changing the algorithm or the interface.

The approach also lacks (currently) support for real world languages. For example support of synchronization
would be necessary to implement the approach for Java. The approach of Zdancewic and Myers supports those
features, but is much more restrictive. Due to the use of observational determinism obviously secure programs
like \texttt{l := 1 || l := 0} are rejected. The approach of Barthe et. al. does not reject those programs and
is in that sense much more permissive.

In the end Barthe et. al. presented a framework with reaches many goals (like permissiveness, statically check-able
and requires no intervention from the programmer) but needs to modify the scheduler interface, which makes it
hard to use for real programs.
